Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-21 Arxiv/main.tex
update arxiv paper

In this work, we design a mechanism for
bayesian inference exploring the idea of calibrating noise using the
same probabilistic distance we want to measure accuracy with. 
We focus on two discrete models, the Beta-Binomial and the
Dirichlet-Multinomial models, and one probability distance, Hellinger distance. 
Our mechanism can be understood as a version of  the exponential mechanism
where the noise is calibrated to the smooth sensitivity of the
utility function, rather than to its global sensitivity. In our
setting, the utility function is the probability distance we want to
use to measure accuracy. To show the usefulness of this mechanism we
show an experimental analysis comparing it with an approach based on
the Laplace mechanism.
\end{abstract}

% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
% \begin{CCSXML}
% <ccs2012>
% <concept>
% <concept_id>10002978.10003029.10011703</concept_id>
% <concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
% <concept_significance>500</concept_significance>
% </concept>
% </ccs2012>
% \end{CCSXML}

% \ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
% % -- end of section to replace with generated code

@@

\section{The Problem Statement}
\label{sec:base}
We are interested in designing a mechanism for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-Multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

\noindent Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$.
Our choice to use Hellinger distance is motivated by two facts, first of all it simplifies
calculations in the case of the probabilistic models considered here
and second of all it also automatically yields bounds on the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
Given two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]
The same change of metric will be applied to the experimental accuracy guarantees.

\section{Mechanisms Introduction}
\label{sec_mechs}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:

\[
  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}
\]

where $\Delta\alpha$ is as defined in Section
\ref{sec_background}. Notice that $\candidateset$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

\subsection{Baseline Mechanisms}
\label{subsec_baselines}

\subsubsection{Exponential Mechanism}
Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
\begin{equation*}
\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\end{equation*}
where $u(x,r)$ is the Hellinger scoring function over candidates, $\hellinger(\bysinfer(\dataobs), r)$, and $GS(x)$ is the global sensitivity calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with global sensitivity. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(x)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(x)})},
\end{equation*}

where local sensitivity is calculated by:

@@

\subsubsection{Laplace Mechanism}
\begin{itemize}
  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$.
  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{\Delta \bysinfer}{\epsilon}}$.
  % \item \todo{$S\propto ||\cdot ||_{1}$}.
  \item $\Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1$.
  \end{itemize}

\subsubsection{Improved Baseline Mechanism}

y using sensitivity 1 in 2 dimensions and 2 in higher dimensions.
    Indeed: we can see the output of the Bayesian inference as a histogram, and $||\bysinfer(\dataobs)-\bysinfer(\dataobs')||_1 \leq 2$.

\subsection{Our Mechanism: Smoothed Hellinger Distance Based Exponential Mechanism $\hexpmech$}
\label{subsec_hexpmech}

\subsubsection{Setting up}

@@

This mechanism also extends to the Dirichlet-Multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-Multinomial system.

@@

\subsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for Laplace mechanism is provided by its probability density function:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t}{b}},
\end{equation*}
where $Y \sim Lap(b)$, $b = \frac{GS}{\epsilon}$

After post-processing:  $Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{t - 1}{b}} - e^{- \frac{t}{b}})$.

\subsection{Accuracy Bound for Exponential Mechanism}
\label{subsec_accuracy_global}
The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
\begin{equation*}
Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
\end{equation*}
where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal results.

@@

In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we consider \emph{balanced} data sets
of observations. This means that in the Beta-Binomial setting the datasets will consist of 50\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d})
the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality and 25\%, 25\%, 25\% and 25\% in 4 dimensionality.
The results show that when the data size increases, the average errors of
$\hexpmech$, Laplace mechanism and decrease. For small datasets,
i.e with size less $300$ in the case of Beta-Binomial models,
both the baseline Laplace mechanisms and improved Laplace mechanism outperform $\hexpmech$.
But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
we considered data sets of the order of 15 thousands elements,
the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved Laplace mechanism.
Similar experimental tendencies were obtained for the Dirichlet-Multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).

@@

\begin{figure*}
\begin{center}
\centering
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size50to100.eps}}
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size100to200.eps}} 
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure*}

>>>>

In this work, we design a mechanism for
bayesian inference exploring the idea of calibrating noise using the
same probabilistic distance we want to measure accuracy with. 
We focus on two discrete models, the Beta-Binomial and the
Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
Our mechanism can be understood as a version of  the exponential mechanism
where the noise is calibrated to the smooth sensitivity of the
utility function, rather than to its global sensitivity. In our
setting, the utility function is the probability distance we want to
use to measure accuracy. To show the usefulness of this mechanism we
show an experimental analysis comparing it with mechanisms based on
the Laplace mechanism.
\end{abstract}

@@

\section{The Problem Statement}
\label{sec:base}
We are interested in designing a mechanism for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\sim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{subsec_baselines}.

Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above. However, this accuracy metric is meaningless when the object released is a distribution rather than a numerical value, and distribution metrics such as $f$-divergence, Hellinger distance, etc. come into mind overtly when we are measuring distance between distributions.

In this work we will use a metric based on a different norm (a distribution metric) to compute the sensitivity
and provide guarantees on the accuracy. 
Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$:
Given two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]

Our choice to use Hellinger distance is motivated by three facts:
\begin{itemize}
\item It simplifies calculations in the case of the probabilistic models considered here.
\item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
\item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy a lot by applying a smooth upper bound on local sensitivity.
\begin{figure}[ht]
\centering
\includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
\caption{\footnotesize{Sensitivity of $\hellinger$}}
\label{fig_sensitivity}
\end{figure}
\end{itemize}

\section{Mechanism Proposition}
\label{sec_mechs}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
\[
  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
\]
where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
Notice that $\candidateset$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

\subsection{Baseline Mechanisms}
\label{subsec_baselines}
Baseline Mechanisms are introduced in prior to our mechanism: $\hexpmech$.

\subsubsection{Exponential Mechanism}
Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
\begin{equation*}
\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\end{equation*}
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(x)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(x)})},
\end{equation*}

where $LS(x)$ is the local sensitivity calculated by:

@@

\subsubsection{Baseline Mechanism - Laplace Mechanism}
 Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:

 \[
 \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \] 
 where $Y \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
 \[
 \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \]
 where $Y_i \sim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model. $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.

 Then release it as the private posterior distribution.

 The sensitivity used in this baseline mechanism is:
 \[
 \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1,
 \]
 which is proportional to the dimensionality.

\subsubsection{Improved Laplace Mechanism}

 Noise added to posterior distribution parameters are scaled to smaller sensitivity in this improved Laplace mechanism. Because in terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.

 Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions:

 \[
 \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \]
 where $Y \sim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
 \[
 \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \]
where $Y_i \sim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.

Both Laplace mechanism and improved one are $\epsilon -$differential privacy\cite{dwork2014algorithmic}.

\subsection{ $\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
\label{subsec_hexpmech}

@@

This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-multinomial system.

@@

\subsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for Laplace mechanism is provided by its probability density function:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t}{b}},
\end{equation*}
where $Y \sim Lap(b)$, $b = \frac{\Delta \bysinfer}{\epsilon}$ in our case.

After post-processing, Laplace noise is discretized. Then the accuracy bound for Laplace mechanism is obtained by:
\[
Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
\]

\subsection{Accuracy Bound for Exponential Mechanism}
\label{subsec_accuracy_global}
The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
\begin{equation*}
Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
\end{equation*}
where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.

@@

In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we consider \emph{balanced} data sets
of observations. This means that in the Beta-Binomial setting the datasets will consist of 50\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d})
the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality and 25\%, 25\%, 25\% and 25\% in 4 dimensionality.
The results show that when the data size increases, the average errors of
$\hexpmech$, Laplace mechanism and decrease. For small datasets,
i.e with size less $300$ in the case of Beta-Binomial models,
both the baseline Laplace mechanisms and improved Laplace mechanism outperform $\hexpmech$.
But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
we considered data sets of the order of 15 thousands elements,
the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved Laplace mechanism.
Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).

@@

\begin{figure}
\begin{center}
\centering
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size50to100.eps}}
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size100to200.eps}} 
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure}
